Restrictive Clearance Comparison

### 2024-03-29 data-raw/RestrictiveClearance_comparison.Rmd
New restrictive clearance updates.

@@

>>>>

# For the invivoPKfit functions, we will hold kelim constant
# This constant will be calculated as CLtot/Vdist (or V1, if 2-compartment)
# This constant is derived by httk in the following way:
calc_total_clearance(dtxsid = common_chems[[10]],
                             restrictive.clearance = FALSE) /
  calc_vdist(dtxsid = common_chems[[10]])

@@

I have modified the starts of the 1- and 2-compartment models,
as well as adding a restrictive_clearance argument in stat_model.

```{r running-invivoPKfit}
minimal_pk <- pk(data = cvt %>%
                   filter(analyte_dtxsid %in% unique(combined_clearance_df$Chemical)),
                 mapping = ggplot2::aes(
                   Chemical = analyte_dtxsid,
                   Chemical_Name = analyte_name_original,
                   DTXSID = analyte_dtxsid,
                   CASRN = analyte_casrn,
                   Species = species,
                   Reference = document_id,
                   Media = conc_medium_normalized,
                   Route = administration_route_normalized,
                   Dose = dose_level_normalized,
                   Dose.Units = "mg/kg",
                   Subject_ID = subject_id,
                   Series_ID = series_id,
                   Study_ID = study_id,
                   ConcTime_ID = conc_time_id,
                   N_Subjects = n_subjects_in_series,
                   Weight = weight_kg,
                   Weight.Units = "kg",
                   Time = time_hr,
                   Time.Units = "hours",
                   Value = conc,
                   Value.Units = "mg/L",
                   Value_SD = conc_sd_normalized,
                   LOQ = loq
                 ))

new_pk <- minimal_pk +
  facet_data(vars(Chemical, Species)) +
  settings_preprocess(keep_data_original = TRUE,
                      suppress.messages = FALSE) +
  settings_optimx(method = c("L-BFGS-B", "bobyqa")) +
  scale_conc(dose_norm = TRUE, log10_trans = FALSE) +
  stat_error_model(error_group = vars(Chemical, Species, Reference)) 
new_pk <- do_data_info(new_pk)

rest_pk <- do_prefit(new_pk, restrictive_clearance = TRUE)
rest_pk <- do_fit(rest_pk, n_cores = 6) # Worked!

nonrest_pk <- do_prefit(new_pk, restrictive_clearance = FALSE)
nonrest_pk <- do_fit(nonrest_pk, n_cores = 6) # Worked!

old_pk <- do_prefit(new_pk, restrictive_clearance = NULL)
old_pk <- do_fit(old_pk, n_cores = 6)

# Unfortunately, it seems the optimizer fails 
# Need to investigate why!!
# Are the kelims calculated too far from those estimated from the data?

rest_wm <- get_winning_model(rest_pk)
rest_AIC <- AIC(rest_pk)
rest_rsq <- rsq(rest_pk)

eval_tkstats(rest_pk) %>% View()
residuals(rest_pk) %>% View()

pl <- plot(rest_pk, n_interp = 12, use_scale_conc = TRUE)
pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "RestrictiveCL_AllFits_Final_202402_08.pdf"),
    height = 6, width = 10)
for (i in 1:nrow(pl)) {
  print(pl$final_plot[[i]])
}
dev.off()

# Non-restrictive fits (constant kelim)

pl <- plot(nonrest_pk, n_interp = 12, use_scale_conc = TRUE)
pdf(file = paste0(Sys.getenv("FIG_DIR"),
              "Non-restrictiveCL_AllFits_Final_202402_08.pdf"),
    height = 6, width = 10)
for (i in 1:nrow(pl)) {
  print(pl$final_plot[[i]])
}
dev.off()

# try dawson
httk::load_dawson2021()
